You can't spell Euphoric without Eu.

### 2018-01-22 article/ms.tex
update before merge

\subsection{Maths}
\label{sec:maths}

Simple mathematics can be inserted into the flow of the text e.g. $2\times3=6$
or $v=220$\,km\,s$^{-1}$, but more complicated expressions should be entered
as a numbered equation:

\begin{equation}
    x=\frac{-b\pm\sqrt{b^2-4ac}}{2a}.
	\label{eq:quadratic}
\end{equation}

Refer back to them as e.g. equation~(\ref{eq:quadratic}).

\subsection{Figures and tables}

Figures and tables should be placed at logical positions in the text. Don't
worry about the exact layout, which will be handled by the publishers.

Figures are referred to as e.g. Fig.~\ref{fig:example_figure}, and tables as
e.g. Table~\ref{tab:example_table}.

@@

\begin{figure}
	% To include a figure from a file named example.*
	% Allowable file formats are eps or ps if compiling using latex
	% or pdf, png, jpg if compiling using pdflatex
	\includegraphics[width=\columnwidth]{example}
    \caption{This is an example figure. Captions appear below each figure.
	Give enough detail for the reader to understand what they're looking at,
	but leave detailed discussion to the main body of the text.}
    \label{fig:example_figure}
\end{figure}

\begin{table}
	\centering
	\caption{This is an example table. Captions appear above each table.
	Remember to define the quantities, symbols and units used.}
	\label{tab:example_table}
	\begin{tabular}{lccr} % four columns, alignment for each
		\hline
		A & B & C & D\\
		\hline
		1 & 2 & 3 & 4\\
		2 & 4 & 6 & 8\\
		3 & 5 & 7 & 9\\
		\hline
	\end{tabular}
\end{table}

@@

\appendix
\newpage
\section{Some extra material}

>>>>

@@

\section{Discussion points}
\begin{itemize}
	\item \textbf{consider CCSN}
	\item \textbf{consider NS-NS}
	\item \textbf{consider the things about our stars that mean it can't be just one of these. i.e differing Rad vels, much different positions, speed travelling vs age of galaxy vs frequency of NS-NS} 
	\item \textbf{consider abundances, lower abundances don't fit NS-NS model, high abundances don't fit CCSN model.}
	\item \textbf{consider then, that the solution is both.}
	\item \textbf{there has to be some kind of statistical argument we can make on this one I reckon, find it.}
\end{itemize}

@@

\appendix
\newpage

\section{Some extra material}
